---
title: "CPI_P1"
author: "Rajwant Mishra"
date: "October 2, 2020"
output:
  html_document:
    code_folding: show
    df_print: paged
    toc: false
    toc_float: false
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
```


<html>
<div><ul>

<li>1/&nbsp;The estimates of employment for 1998-2006 are based on the 2002 North American Industry Classification System (NAICS). The estimates for 2007-2010 are based on the 2007 NAICS. The estimates for 2011-2016 are based on the 2012 NAICS. The estimates for 2017 forward are based on the 2017 NAICS.</li>
<li>2/&nbsp;Excludes limited partners.</li>
<li>3/&nbsp;Under the 2007 NAICS, internet publishing and broadcasting was reclassified to other information services.</li>
<li>(D)&nbsp;Not shown to avoid disclosure of confidential information; estimates are included in higher-level totals.</li>
<li>(T)&nbsp;Estimate for employment suppressed to cover corresponding estimate for earnings. Estimates for this item are included in the total.</li>
<li>(NA)&nbsp;Not available.</li>
<li>(NM)&nbsp;Not meaningful.</li>
<li> &nbsp;Last updated: September 24, 2019-- new statistics for 2018; revised statistics for 2014-2017.</li>
</ul></div>
</html>

```{r message=FALSE, warning=FALSE}
EMP_DATA_FILE <- "EMP9818.csv"
EMP_DATA <- read_delim(EMP_DATA_FILE,delim = ",",col_names = TRUE,trim_ws= TRUE)#,skip = 6,col_types = list(col_character(),col_character(),col_character(),col_character(),col_character(),col_character(),col_character(),col_character(),col_character(),col_character(),col_character(),col_character(),col_character(),col_character(),col_character(),col_character()))

# names(SAP_INV_DAT) = c("DROP","I_BILLDATE","I_ORG","I_DC","I_DOCCA","I_BILLTYPE","I_ORDER_REA","I_DIV","I_MATYPE","I_BILL_QTY","BLANK")
# SAP_INV_DAT<- SAP_INV_DAT[-which(is.na(SAP_INV_DAT$I_ORG)),] %>% .[-str_which(trimws(.$I_ORG),'SOrg.|-----'),c(-1,-11)]
# 
# SAP_INV_DAT$I_BILLDATE <- date(parse_datetime(SAP_INV_DAT$I_BILLDATE, "%m/%d/%Y"))
# 
# head(SAP_INV_DAT)

summary(EMP_DATA)



# MN-MAIN  | NN - RANGE  | NL - LAST |
EMAP_CAT_LAST <- EMP_DATA[,c(2,5,6,7)] %>% filter(GeoName=="United States") %>% mutate(ISM = ifelse(IndustryClassification=="...","M","N")) %>%  separate(IndustryClassification, c("From", "To"))  %>% mutate(ISML = ifelse(is.na(To)==T,"L","N")) %>% filter(ISML=="L") %>%  select(.,LineCode,Description)

EMP_DAT_CAT <- EMP_DATA[,c(2,5,9:29)] %>% left_join(EMAP_CAT_LAST,.,by="LineCode")

# Reading the Category and deatail Desc for ref.
IND_DESC <- XML::xmlToDataFrame("SAEMP25N__definition.xml")
names(IND_DESC) <- c("LineCode","Description")

glimpse(EMP_DAT_CAT)
head(EMP_DAT_CAT,130)

glimpse(IND_DESC)
head(IND_DESC,5)

# # Other Range data 
# EMP_DATA[,c(2,5,6,7)] %>% filter(GeoName=="United States") %>% mutate(ISM = ifelse(IndustryClassification=="...","M","N")) %>%  separate(IndustryClassification, c("From", "To"))  %>% mutate(ISML = ifelse(is.na(To)==T,"L","N")) %>% filter(ISM=="M") 
# 
# EMP_DATA %>% filter(GeoName=="United States") %>% .[,c(5,7)] %>% mutate(ISM = ifelse(IndustryClassification=="...","M","N")) %>%  separate(IndustryClassification, c("From", "To"))  %>% mutate(ISML = ifelse(is.na(To)==T,"L","N")) %>% filter(ISM=="N" & ISML=="N") 






```

```{r}
temp_name <- names(EMP_DAT_CAT [,c(4:24)])
EMP_DAT_CAT_SAN <-  data.frame(lapply(EMP_DAT_CAT [,c(4:24)],function(x) {
                 gsub("(D)|(T)",NA,x)
              })) 

names(EMP_DAT_CAT_SAN) = temp_name

EMP_DAT_CAT_SAN <- cbind(EMP_DAT_CAT[,c(1:3)],EMP_DAT_CAT_SAN)

EMP_DAT_CAT_SAN
```

```{r}
EMP_DAT_CAT_SAN %>% filter(GeoName=="New York")
```

